### 2018-12-10 paper/paper.tex
add extract figure, fix references

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{sectsty}
\usepackage{multicol, caption}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subfig}
%\usepackage{subcaption}

%\usepackage{biblatex}
\usepackage[margin=0.5in]{geometry} % don't know what size margins to use
\newenvironment{Figure}
  {\par\medskip\noindent\minipage{\linewidth}}
  {\endminipage\par\medskip}

\setlength{\columnsep}{1cm}
%\addbibresource{paper.bib}
%\nocite{*}
\sectionfont{\fontsize{12}{15}\selectfont}

@@

            \begin{Figure}
                \centering
                \includegraphics[width=\linewidth]{figures/process.png}
                \captionof{figure}{Our Machine Learning Process}
                \label{fig:process}
            \end{Figure}

@@

            So we shortlisted a few datasets that fulfilled some of these characteristics, but
            settled on the SpamAssasin Dataset which fulfilled all of our requirements
            with raw email data that mostly consisted of both business and casual
            conversations. It consisted of both easy and hard data, but we stuck with
            just the easy data as many of the hard pieces of data were too difficult
            to classify without more information about the user.

@@

            \begin{Figure}
                \centering
                \includegraphics[width=\linewidth]{figures/prep.png}
                \captionof{figure}{Preparation Process}
                \label{fig:preprocess}
            \end{Figure}

@@

            The next step is to extract the necessary features and then vectorize
            them for training with our classifier. The first step of extraction was
            to

            \begin{minipage}{0.4\columnwidth}
                \includegraphics[width=\textwidth]{figures/spam_wc}
                \captionof{figure}{Spam}
                \label{spam_wc}
            \end{minipage}
            \begin{minipage}{0.4\columnwidth}
                \includegraphics[width=\textwidth]{figures/ham_wc}
                \captionof{figure}{Ham}
                \label{ham_wc}
             \end{minipage}
            This is more text
        %\section{Classifier Selection}

@@

        %\section{Conclusion}

        %\section{References}
        % \printbibliography
    \end{multicols}
\end{document}

>>>>

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{sectsty}
\usepackage{multicol, caption}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subfig}

\usepackage[margin=0.5in]{geometry} % don't know what size margins to use
\newenvironment{Figure}
  {\par\medskip\noindent\minipage{\linewidth}}
  {\endminipage\par\medskip}

\setlength{\columnsep}{1cm}

\sectionfont{\fontsize{12}{15}\selectfont}

@@

            \begin{Figure}
                \centering
                \includegraphics[width=\linewidth]{figures/process.png}
                \captionof{figure}{Our Machine Learning Process}\label{fig:process}
            \end{Figure}

@@

            So we shortlisted a few datasets that fulfilled some of these characteristics, but
            settled on the SpamAssasin Dataset which fulfilled all of our requirements
            with raw email data that mostly consisted of both business and casual
            conversations\cite{sa_dataset}. It consisted of both easy and hard data, but we stuck with
            just the easy data as many of the hard pieces of data were too difficult
            to classify without more information about the user.

@@

            \begin{Figure}
                \centering
                \includegraphics[width=\linewidth]{figures/prep.png}
                \captionof{figure}{Preparation Process}\label{fig:preprocess}
            \end{Figure}

@@

            The next step is to extract the necessary features and then vectorize
            them for training with our classifier.

            \begin{Figure}
                \centering
                \includegraphics[scale=0.5]{figures/extract.png}
                \captionof{figure}{Extraction Process}
                \label{fig:extrac}
            \end{Figure}

            The first step of extraction was
            to find words that meant the most to the corpus which we defined as
            the body of the email. To accomplish this
            we used the tf-idf algorithm implemented in scikit-learn. This algorithm helps
            weigh down words that are too common, and bring up words that are important
            to the corpus. Next we split the documents into spam and ham before analysis.
            This was done because this algorithm is still based on frequency and the
            ratio of ham to spam was not 1:1. Characteristic words to spam emails such
            as ``free'' wouldn't show up because they're not prominent in ham emails.

            \begin{minipage}{0.4\columnwidth}
                \includegraphics[width=\textwidth]{figures/spam_wc}
                \captionof{figure}{Spam}\label{fig:spam_wc}
            \end{minipage}
            \begin{minipage}{0.4\columnwidth}
                \includegraphics[width=\textwidth]{figures/ham_wc}
                \captionof{figure}{Ham}\label{fig:ham_wc}
             \end{minipage}

             Figures \ref{fig:spam_wc} and \ref{fig:ham_wc} show
             the most prominent 50 words in the corpus. Most the the words in the
             ham word cloud relate to business operations asking someone to do about
             task or getting times and dates of events. When you look at the spam
             word cloud you see a few similar words such as ``mail'' or ``get''.
             But in general you see words that you would associate with someone trying
             to get you to send them money or buy a product. Words like ``money'',
             ``offer'' and ``order'' are the epitome of this.
        %\section{Classifier Selection}

@@

        \section{Conclusion}

        \nocite{*}
        \bibliography{paper} 
        \bibliographystyle{alpha}
    \end{multicols}
\end{document}
